---
title: "Laralee_Harkleroad_ProgressReport2"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(haven)
library(readxl)
library(forcats)
library(RColorBrewer)
library(knitr)
library(plotly)
library(Metrics)
library(modelr)
library(rvest)
library(acs)
library(lubridate)
library(noncensus)
library(tigris)
```
The above code sets up the file. I went ahead and loaded every library we have worked with thus far just to be on the safe side.

#1 Code that accesses a dataset that contains your dependent variable.
```{r}
delta <-read.csv('/Users/lfhar/OneDrive/8200 Data Science/scripts_data_files/delta_public_release_00_15.csv',header = TRUE)
```
The above code loads the data from Delta that has been saved in a CSV file.

```{r}
View(delta)
```
The above code views the data.

```{r}
save(delta,file="delta.Rdata")
```
The above code saves the data as an Rdata file.


#2 A univaraiate graphic describing the dependent variable.
```{r}
gg<-ggplot(delta,aes(x=acadsupp01))
gg<-gg+geom_histogram(fill="lightblue")
gg
``` 
The above code creates a histogram graphic describing the dependent variable of academic support spending. 

#3 The conditional mean of your dependent variable at levels of at least one independent variable.
```{r}
delta_sum<-delta%>%
  group_by(total03_revenue)%>%
  summarize(acadsupp01_avg=mean(acadsupp01))

delta_sum
```
The above code interprets the conditional mean of academic support spending as a function of total revenues.

```{r}
delta_sum<-delta%>%
  group_by(govt_reliance_c)%>%
  summarize(acadsupp01_avg=mean(acadsupp01))

delta_sum
```
The above code interprets the conditional mean of academic support spending as a function of institutional reliance on governmental funding.

```{r}
delta_sum<-delta%>%
  group_by(total03_revenue,govt_reliance_c)%>%
  summarize(acadsupp01_avg=mean(acadsupp01_avg))

## Get the results
delta_sum
```
The above code interprets the conditional mean of academic support spending as a function of both total revenues received and institutional reliance on governmental funding.

#4 A bivariate graphic that compares your dependent variable with at least one other independent variable.
```{r}
delta_sum<-delta%>%
  group_by(govt_reliance_c)%>%
  summarize(acadsupp01_avg=mean(acadsupp01))

delta_sum
## Now a dot plot
gg<-ggplot(delta_sum,aes(x=reorder(govt_reliance_c,-acadsupp01_avg),y=acadsupp01_avg))
gg<-gg+geom_point(color="orange",size=5)
gg<-gg+xlab("Reliance on Government Support")+ylab("Average Academic Support Expenses")
gg<-gg+coord_flip()

gg
```
The above code creates a dot plot comparing average academic support expenses with institutional reliance on government support.

